### 2025-07-17 title_page.Rmd
title page

**hatchR** is an open-source software environment distributed via CRAN and additional details hosted at software website (<https://bmait101.github.io/hatchR/>). Reproducible methods for this manuscript are available at the manuscript github (<https://github.com/morgan-sparks/hatchR_nonfish>) in the `paper.Rmd` file. The repository will become public and publicly archived with a DOI at acceptance of the manuscript.

>>>>

**hatchR** is an open-source software environment distributed via CRAN and additional details are hosted at software website (<https://bmait101.github.io/hatchR/>). Reproducible methods for this manuscript are available at the manuscript github (<https://github.com/morgan-sparks/hatchR_nonfish>) in the `paper.Rmd` file. The repository will become public and publicly archived with a DOI at acceptance of the manuscript.
